Removal only

### 2020-05-29 analysis/figure-4.Rmd
better exp desig fig 4

  p <- df %>%
    dplyr::filter(gene  == whichgene, 
                  treatment %in% removallevels)  %>%
    ggplot(aes(y =  counts, x = treatment, fill = treatment, color = sex)) +
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(size = 0.25, aes(color = sex)) +
    theme_B3() +
    theme(legend.position = "none",
          axis.title.x = element_blank(),
          plot.subtitle = element_text(face = "italic")) +
    scale_color_manual(values = allcolors) +
    scale_fill_manual(values = allcolors)  +
    labs(title = paste(whichtissue, sep = " "), subtitle = whichgene, y = "gene expression") +
    geom_signif(comparisons = list(c( "inc.d3", "m.inc.d3"),
                                   c( "inc.d9", "m.inc.d9"),
                                   c( "inc.d17", "m.inc.d17"),
                                   c( "hatch", "m.n2")),
                map_signif_level=TRUE,
                textsize = 3, family = 'Helvetica',
                vjust = 1.5, size = 0.5) 
  return(p)

@@

a <- plotcandidateremoval(hypvsd, "HTR2C", "hypothalamus") + theme(axis.title.x = element_blank(), axis.text.x = element_blank())
b <- plotcandidateremoval(pitvsd, "PRL", "pituitary")+ theme(axis.title.x = element_blank(), strip.text = element_blank(), axis.text.x = element_blank())
c <- plotcandidateremoval(gonvsd, "ESR2", "gonads") + theme(strip.text = element_blank())
boxplots1 <- plot_grid(a,b,c, nrow = 3)

@@

  p <- df %>%
    dplyr::filter(gene  == whichgene, 
                  treatment %in% timinglevels,
                  !treatment %in%  c("control", "bldg", "inc.d3"))  %>%
    ggplot(aes(y =  counts, x = treatment, fill = treatment, color = sex)) +
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(size = 0.25, aes(color = sex)) +
    theme_B3() +
    theme(legend.position = "none",
          axis.title.x = element_blank(),
          plot.subtitle = element_text(face = "italic")) +
    scale_color_manual(values = allcolors) +
    scale_fill_manual(values = allcolors)  +
    labs(title = paste(whichtissue, sep = " "), subtitle = whichgene, y = "gene expression") +
    geom_signif(comparisons = list(c("inc.d9", "early"), 
                                  c( "inc.d17", "prolong"), c( "prolong", "hatch"),
                                  c( "hatch", "extend"), c( "n5", "extend")),
                map_signif_level=TRUE,
                textsize = 3, family = 'Helvetica',
                vjust = 1.5, size = 0.5) 
  return(p)

@@

e <- plotcandidatetiming(hypvsd, "HTR2C", "hypothalamus") + theme(axis.title.x = element_blank(), axis.text.x = element_blank()) 
f <- plotcandidatetiming(pitvsd, "PRL", "pituitary")+ theme(axis.title.x = element_blank(), strip.text = element_blank(), axis.text.x = element_blank())
g <- plotcandidatetiming(gonvsd, "ESR2", "gonads") + theme(strip.text = element_blank())
boxplots2 <- plot_grid(e,f,g, nrow = 3)
```

@@

boxplots <- plot_grid(boxplots1, boxplots2, nrow = 1, rel_widths = c(1.5,1),
                      labels = "AUTO", label_size = 8)
fig4 <- plot_grid(boxplots, design, t456, ncol = 1, rel_heights = c(2.75,1,1),
                      labels = c(" ", " " , "C"), label_size = 8)
fig4

>>>>

  p <- df %>%
    dplyr::filter(gene  == whichgene, 
                  treatment %in% removallevels)  %>%
    ggplot(aes(y =  counts, x = treatment, fill = treatment, color = sex)) +
    geom_boxplot(outlier.shape = NA, lwd=0.5) +
    geom_jitter(size = 0.25, aes(color = sex)) +
    theme_B3() +
    theme(legend.position = "none",
          axis.title.x = element_blank(),
          plot.subtitle = element_text(face = "italic")) +
    scale_color_manual(values = allcolors) +
    scale_fill_manual(values = allcolors)  +
    labs(title = paste(whichtissue, sep = " "), subtitle = whichgene, y = "gene expression") +
    geom_signif(comparisons = list(c( "inc.d3", "m.inc.d3"),
                                   c( "inc.d9", "m.inc.d9"),
                                   c( "inc.d17", "m.inc.d17"),
                                   c( "hatch", "m.n2")),
                map_signif_level=TRUE,
                textsize = 1.5, family = 'Helvetica',
                vjust = 1.5, size = 0.5) 
  return(p)

@@

a <- plotcandidateremoval(hypvsd, "HTR2C", "hypothalamus") + theme(axis.title.x = element_blank())
b <- plotcandidateremoval(pitvsd, "PRL", "pituitary")+ theme(axis.title.x = element_blank(), strip.text = element_blank())
c <- plotcandidateremoval(gonvsd, "ESR2", "gonads") + theme(strip.text = element_blank())
boxplots1 <- plot_grid(a,b,c, nrow = 3)

@@

  p <- df %>%
    dplyr::filter(gene  == whichgene, 
                  treatment %in% timinglevels,
                  !treatment %in%  c("control", "bldg", "inc.d3"))  %>%
    ggplot(aes(y =  counts, x = treatment, fill = treatment, color = sex)) +
    geom_boxplot(outlier.shape = NA, lwd=0.5) +
    geom_jitter(size = 0.25, aes(color = sex)) +
    theme_B3() +
    theme(legend.position = "none",
          axis.title.x = element_blank(),
          plot.subtitle = element_text(face = "italic")) +
    scale_color_manual(values = allcolors) +
    scale_fill_manual(values = allcolors)  +
    labs(title = paste(whichtissue, sep = " "), subtitle = whichgene, y = "gene expression") +
    geom_signif(comparisons = list(c("inc.d9", "early"), 
                                  c( "inc.d17", "prolong"), c( "prolong", "hatch"),
                                  c( "hatch", "extend"), c( "n5", "extend")),
                map_signif_level=TRUE,
                textsize = 1.5, family = 'Helvetica',
                vjust = 1.5, size = 0.5) 
  return(p)

@@

e <- plotcandidatetiming(hypvsd, "HTR2C", " ") + theme(axis.title.x = element_blank()) + labs(y = NULL, subtitle = " ", title = " ") 
f <- plotcandidatetiming(pitvsd, "PRL", "pituitary")+ theme(axis.title.x = element_blank(), strip.text = element_blank()) + labs(y = NULL, subtitle = " ", title = " ") 
g <- plotcandidatetiming(gonvsd, "ESR2", "gonads") + theme(strip.text = element_blank()) + labs(y = NULL, subtitle = " ", title = " ") 
boxplots2 <- plot_grid(e,f,g, nrow = 3)
boxplots2
```

@@

boxplots <- plot_grid(boxplots1, boxplots2, nrow = 1, rel_widths = c(1.5,1),
                      labels = "AUTO", label_size = 8)
fig4 <- plot_grid(boxplots, design, t456, ncol = 1, rel_heights = c(2.75,1.3,1),
                      labels = c(" ", " " , "C"), label_size = 8)
fig4
